% arara: pdflatex
%
% Kenneth Hanson's Resume
% Created: 6/4/2012
% Based on Andrew McNabb's template (http://www.mcnabbs.org/andrew/linux/latexres/)

\newcommand{\editdate}{03/10/2021}

\documentclass[10pt,oneside]{article}

\input{cv-preamble}


\begin{document}

\topheading

\ressection{Education}

\begin{reslist}
	\resbigitem{PhD, Linguistics}
		{08/2020--Present}
		{Stony Brook University, Stony Brook, NY}
		{}
	\resbigitem{BA, Linguistics}
		{01/2011--05/2014}
		{Michigan State University, East Lansing, MI}
		{}
	\begin{itemize}
		\item Additional Major in Japanese. Minor in Computer Science. Cumulative GPA: 4.0.
	\end{itemize}
	
%	\resbigitem{2013 LSA Linguistic Institute}
%		{06/2013--07/2013}
%		{University of Michigan, Ann Arbor, MI}
%		{}
\end{reslist}


\ressection{Positions}

\ressubsection{Research}

\begin{reslist}
	\resbigitem{Undergraduate Research Assistant}
		{09/2012--05/2014}
		{Dept.\ of Linguistics and Languages, Michigan State University}
		{}
	\begin{itemize}
		\item For Cristina Schmitt, PhD and Alan Munn, PhD%, Dept.\ of Linguistics and Languages
%		\item Partially funded by the MSU College of Arts and Letters Undergraduate Research Initiative (CAL-URI).
	\end{itemize}
	
	\resbigitem{Undergraduate Research Assistant}
		{05/2012--06/2013}
		{Dept.\ of Computer Science and Engineering, Michigan State University}
		{}
	\begin{itemize}
		\item For Joyce Chai, PhD%, Dept.\ of Computer Science and Engineering
%		\item Funded by the MSU Engineering Summer Undergraduate Research Experience Program (EnSURE) for Summer 2012.
	\end{itemize}
\end{reslist}

\ressubsection{Teaching}

\begin{reslist}
	\resbigitem{Graduate Teaching Assistant}{08/2020--Present}
		{Stony Brook University}{}
	\begin{itemize}
		\item LIN 101 (Human Language) -- Spring 2021
		\item LIN 120 (Language and Technology) -- Fall 2020
	\end{itemize}
	
	\resbigitem{Undergraduate Teaching Assistant}{01/2012-05/2013}
		{Michigan State University}{}
	\begin{itemize}
		\item CSE 232 (Intro to Programming II) -- Spring 2012, Fall 2012, Spring 2013
	\end{itemize}
\end{reslist}

\ressubsection{Non-Academic Employment}

\begin{reslist}
	\resbigitem{Assistant English Teacher}
		{08/2014-08/2018}
		{Japan Exchange and Teaching (JET) Programme}
		{}
\end{reslist}


\ressection{Publications}

\begin{publist}
	\item[2014] {Chai, J. Y., L. She, R. Fang, S. Ottarson, C. Littley, C. Liu, and K. Hanson. Collaborative Effort towards Common Ground in Situated Human Robot Dialogue. 2014 ACM/IEEE International Conference on Human-Robot Interaction (HRI). Bielefeld, Germany.}
\end{publist}


\ressection{Presentations}

\ressubsection{Refereed Conference Posters}
\begin{publist}
	\item[2014] {Hanson, Kenneth, Cristina Schmitt, and Alan Munn. The loss of bare singular arguments and predicates in the history of English. 16th Diachronic Generative Syntax (DiGS) Conference. Budapest, Hungary.}
\end{publist}

\ressubsection{Refereed Undergraduate Conference Talks}
\begin{publist}
	\item[2014] {Hanson, Kenneth, Cristina Schmitt, and Alan Munn. The loss of bare singular noun phrases in the history of English. Great Lakes Expo for Experimental and Formal Undergraduate Linguistics (GLEEFUL). Michigan State University, East Lansing, MI.}
\end{publist}

\ressubsection{Other Undergraduate Conference Presentations}
\begin{publist}
	\item[2014] {Hanson, Kenneth. Quantitative methods for the analysis of Classical Japanese poetry. Michigan State Undergraduate Linguistics Conference (MSULC). Michigan State University, East Lansing, MI.}
	
	\item[2014] {Hanson, Kenneth. Methods for tracking lexical classes in parsed historical corpora. Poster presented at the Michigan State Undergraduate Linguistics Conference (MSULC). Michigan State University, East Lansing, MI.}
	
	\item[2013] {Hanson, Kenneth. CorpusExtract: a tool for analyzing syntactically annotated corpora. Poster presented at the Michigan State Undergraduate Linguistics Conference (MSULC). Michigan State University, East Lansing, MI.}
	
	\item[2012] {Hanson, Kenneth. Playing a naming game with Darwin: towards human-robot dialog. Summer Undergraduate Research Forum (SURF). Michigan State University, East Lansing, MI.}
\end{publist}


\ressection{Other Activities}

\begin{reslist}
	\resbigitem{Author and Webmaster}
		{06/2011--Present}
		{JapaneseProfessor.com}
		{}
	
	\resbigitem{Vice President, Secretary, and Activities Director}
		{02/2012--05/2014}
		{q Undergraduate Association for Linguistics at Michigan State (qUALMS)}
		{}
\end{reslist}


\ressection{Awards and Honors}
	
\ressubsection{Funded Awards}
\begin{reslist}
	\resbigitem{Graduate Council Fellowship}
		{08/2020-05/2025}
		{Stony Brook University}
		{}
	\resbigitem{Board of Trustees Scholarship Award}
		{05/2014}
		{Michigan State University}
		{}
	\resbigitem{Outstanding Senior Achievement Award}
		{05/2014}
		{MSU College of Arts and Letters }
		{}
	\resbigitem{Engineering Summer Undergraduate Research Experience (EnSURE)}
		{05-07/2012}
		{MSU College of Engineering}
		{}
	\resbigitem{Mitsui USA/Community Scholarship for YFU Study Abroad in Japan}
		{06--07/2009}
		{Mitsui USA Foundation}
		{}
\end{reslist}

\ressubsection{Other Awards}
\begin{reslist}
	\resbigitem{Presentation Award}
		{04/2014}
		{MSULC, Michigan State University, East Lansing, MI}
		{}
\end{reslist}

%\ressubsection{Honor Societies}
%\begin{itemize}
%	\resitem{Phi Beta Kappa}{2014--Present}
%	\resitem{AAJT Japanese National Honor Society College Chapter}{2014--Present}
%\end{itemize}


%\ressection{Skills and Additional Information}
%
%\begin{itemize}
%	\item \textbf{Languages} -- English (native), Japanese (advanced, passed JLPT N2 in Dec. 2013).
%	
%	\item \textbf{Programming} -- Experienced: Python, C++. Familiar: Java, R, Qt, wxWidgets, ANTLR3, Make, Git, SVN. Basic knowledge: Bash, x86, SPARC.
%	
%	\item \textbf{Misc.\ Computing} -- Experienced: Ubuntu Linux, \LaTeX{}, CorpusSearch. Familiar: Wordpress, HTML/CSS, ConTeXt.
%	
%	\item \textbf{Music} --  Piano (advanced), marimba (advanced), and some composition.
%	
%	\item \textbf{Volunteer} -- Michigan Japanese Quiz Bowl (03/2012--03/2014)
%\end{itemize}


\end{document}
